Automating Verification of MPC Security

### 2023-06-09 popl24/composition.tex
checkpoint

\section{A Protocol Metalanguage}
\label{section-metalang}

$$
\begin{array}{rcl@{\hspace{8mm}}r}
\flab &\in& \mathrm{Field}\\
x &\in& \mathrm{EVar}\\
f &\in& \mathrm{FName}\\[2mm]
e &::=& b \mid \flip{e}{e} \mid \secret{e}{e} \mid \view{e}{e} \mid \oracle{e} \mid \enot\ e \mid e\ \eand\ e \mid e\ \exor\ e \mid & \textit{expressions}\\[0mm]
& & \select{e}{e}{e} \mid 
\send{\view{e}{e}}{e} \mid \send{\view{e}{e}}{\OT{e}{e}{e}} \mid e;e \mid \\[0mm]
& & x \mid \elet{x}{e}{e} \mid f(e,\ldots,e) \mid \{ \flab = e; \ldots; \flab = e \}
\mid e.\flab \mid e\ttt{||}e \mid (e) \\[2mm]
v &::=& w \mid \cid \mid \be \mid \{ \flab = v;\ldots;\flab = v \} 
\mid (\,) & \textit{values}\\[2mm]
{fn} &::=& f(x,\ldots,x) \{ e \} & \textit{functions}
\end{array}
$$

\begin{definition}
A \emph{codebase} $\codebase$ is a list of function 
declarations. We write $ \codebase(f) = x_1,\ldots,x_n,\ e$
iff $f(x_1,\ldots,x_n) \{ e \} \in \codebase$.
A \emph{metaprogram}, aka \emph{mataprotocol} is a pair of a 
codebase and expression $\codebase, e$. We may omit
$\codebase$ if it is clear from context.  
\end{definition}

$$
\begin{array}{rcl@{\hspace{3mm}}r}
E &::=& [\,] \mid \enot\ E \mid E\ \bop\ e \mid v\ \bop\ E \mid & \textit{evaluation contexts}\\[1mm]
& & \flip{E}{e} \mid \secret{E}{e} \mid \view{E}{e} \mid \oracle{E} \mid  \\[1mm]
& & \flip{\cid}{E} \mid \secret{\cid}{E} \mid \view{\cid}{E} \mid \send{E}{e} \mid \send{\view{\cid}{w}}{E}\\[1mm]
& & \OT{E}{e}{e} \mid \OT{v}{E}{e} \mid \OT{v}{v}{E} \mid\\[1mm]
& & \select{E}{e}{e} \mid \select{v}{E}{e} \mid \select{v}{v}{E} \mid\\[1mm]
& & \elet{x}{E}{e} \mid f(v,\ldots,v,E,e,\ldots,e) \mid \\[1mm]
& & \{ \flab = v;\ldots;\flab = v;\flab = E;\flab = e;\ldots;\flab = e \} \mid E.\flab \mid E\ttt{||}e \mid v \ttt{||}E
\end{array}
$$

$$
\begin{array}{rcl@{\hspace{10mm}}r}
\config{\prog}{\elet{x}{v}{e}} &\redx& \config{\prog}{e[v/x]}\\
\config{\prog}{f(v_1,...,v_n)} &\redx&
\config{\prog}{e[v_1/x_1,\ldots,v_n/x_n]} & 
 \codebase(f) = x_1,\ldots,x_n,\ e\\
\config{\prog}{\{\ldots; \flab = v; \ldots\}.\flab} &\redx&
 \config{\prog}{v}\\
 \config{\prog}{w_1\ttt{||}w_2} &\redx& \config{\prog}{w_1w_2}\\
 \config{\prog}{v;e} &\redx& \config{\prog}{e}\\
\config{\prog}{\instr} &\redx& \config{\prog;\instr}{()}\\
\config{\prog}{E[e]} &\redx& \config{\prog'}{E[e']} & \text{if}\ \config{\prog}{e} \redx \config{\prog'}{e'} 
\end{array}
$$

\subsection{Compositional Properties: Garbled $\NIMO$}

>>>>

\section{Compositional Properties: Garbled $\NIMO$}
\label{section-composition}

### 2023-06-09 popl24/hyperprop.tex
checkpoint

Finally, consider our secure communications example, that we call program
$\prog_3$. We will assume that $H = \{ 1,2 \}$ and $C = \{ 0 \}$, so
the adversary has access to $\vx{0}{0}$ in particular:
\begin{verbatimtab}
v[2,0] := f[1,0];
v[0,0] := f[1,0] xor s[1,0];
v[2,1] := v[0,0];
v[2,2] := v[2,1] xor v[2,0]
\end{verbatimtab}
First, let's focus on information available to the adversary
about the secret $\sx{1}{0}$ (aside from its publicly-known marginal
distribution). We will consider the marginal distribution
of $\sx{1}{0}$ and $\vx{0}{0}$:
\begin{mathpar}
X \defeq \{ \vx{0}{0}, \sx{1}{0} \}

\pdf{X} \defeq \margd{\progd(\prog_3)}{X}
\end{mathpar}
Since the adversary can directly observe the value in $\vx{0}{0}$ in
any given run, we therefore consider the distribution conditioned on
that value. As we can see, this shows that the protocol reveals
no information about the secret:
\begin{mathpar}
  \condd{(\pdf{X}}{\{ \vx{0}{0} \mto 0\})}(\{ \sx{1}{0} \mapsto 0\}) = .5

  \condd{(\pdf{X}}{\{ \vx{0}{0} \mto 0\})}(\{ \sx{1}{0} \mapsto 1\}) = .5

  \condd{(\pdf{X}}{\{ \vx{0}{0} \mto 1\})}(\{ \sx{1}{0} \mapsto 0\}) = .5

  \condd{(\pdf{X}}{\{ \vx{0}{0} \mto 1\})}(\{ \sx{1}{0} \mapsto 1\}) = .5
\end{mathpar}

Now, let's focus on the information directly available to honest parties,
and specifically the information available through $\vx{2}{2}$ about
$\sx{1}{0}$. We first define the relevant marginal distribution:
\begin{mathpar}
X \defeq \{ \vx{2}{2}, \sx{1}{0} \}

\pdf{X} \defeq \margd{\progd(\prog_3)}{X}
\end{mathpar}
Then we consider the marginal distribution of the secret conditioned
on the view $\vx{2}{2}$, which shows the direct correlation and therefore
correctness. 
\begin{mathpar}
  \condd{(\pdf{X}}{\{ \vx{0}{0} \mto 0\})}(\{ \sx{1}{0} \mapsto 0\}) = 1

  \condd{(\pdf{X}}{\{ \vx{0}{0} \mto 0\})}(\{ \sx{1}{0} \mapsto 1\}) = 0

  \condd{(\pdf{X}}{\{ \vx{0}{0} \mto 1\})}(\{ \sx{1}{0} \mapsto 0\}) = 0

  \condd{(\pdf{X}}{\{ \vx{0}{0} \mto 1\})}(\{ \sx{1}{0} \mapsto 1\}) = 1
\end{mathpar}

@@

%\newcommand{\outv}{\mathit{out}}

>>>>

As we've discussed in our section on Related Work
(\ref{section-related}), previous authors have noted connections
between the traditional formulation of the MPC security model- aka the
simulator security model- and hyperproperty-style formulations of
program trace behavior \cite{XXX} including probabilistic
noninterference. This formulation of hyperproperties that are at least
sound with respect to simulator security bridges a conceptual gap
between foundational approaches to security, and also motivates and
supports automated analysis \cite{XXX}.

In this section we formulate a new hyperproperty that we show is sound
for passive security in the real/ideal model, called
\emph{noninterference modulo output ($\NIMO$)}. We do not claim
completeness with respect to passive security, but soundness
guarantees that enforcement of $\NIMO$ in our analyses implies passive
security. In Section \section{section-bruteforce} we show how $\NIMO$ can
be automatically enforced in a brute-force manner, and in
Section \section{section-bruteforce}

@@

### 2023-06-09 popl24/metalang.tex
checkpoint

\section{A Protocol Metalanguage}

@@

\begin{verbatimtab}
andgg(g, wla, wlb, wlc, wva, wvb) {
andgate(g, wla, wlb, wlc);
evalgate(g, wva, wvb)
}
\end{verbatimtab}

\begin{lemma}[Input Encoding]
Assume given the following evaluation relation:
$$
\config{\prog_1}{E[\ttt{encode}(w,v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
$$
If there exists gate identifiers $g_1, g_2$ such that:
\begin{enumerate}
  \item $g_1 \ne g_2 \wedge g_1,g_2 \not\in \gates(\prog_1)$
  \item $\owl(\prog_1,v_1,g_1) \wedge \owl(\prog_1,v_2,g_2)$
  \item $\gNIMO(\prog_1,v.\ttt{wv1},g_1) \wedge \gNIMO(\prog_1,v.\ttt{wv2},g_2)$
\end{enumerate}
then:
\begin{enumerate}
\item $g_1,g_2 \in  \gates(\prog_2)$
\item $\gNIMO(\prog_1;\prog_2,v.\ttt{wv1},g_1) \wedge \gNIMO(\prog_1;\prog_2,v.\ttt{wv2},g_2)$
\item $$(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$$
\end{enumerate}
\end{lemma}

\begin{lemma}[Composition ($\eand$)]
Assume given the following evaluation relation:
$$
\config{\prog_1}{E[\ttt{andgg}(g,v_1,\ldots,v_5)]} \redxs \config{\prog_1;\prog_2}{E[v_6]}
$$
If there exist gate identifiers $g_1, g_2$ such that:
\begin{enumerate}
  \item $g_1 \ne g_2 \ne g \wedge g_1,g_2 \in \gates(\prog_1) \wedge g \not\in \gates(\prog_1)$
  \item $\owl(\prog_1,v_1,g_1) \wedge \owl(\prog_1,v_2,g_2) \wedge \owl(\prog_1,v_3,g)$
  \item $\gNIMO(\prog_1,v_4,g_1) \wedge \gNIMO(\prog_1,v_5,g_2)$
\end{enumerate}
then:
\begin{enumerate}
  \item $g \in \gates(\prog_2)$
  \item $\gNIMO(\prog_1;\prog_2,v_6,g)$
  \item $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
\end{enumerate}
\end{lemma}

\begin{lemma}[Decoding]
Assume given the following evaluation relation:
$$
\config{\prog_1}{E[\ttt{decoder}(v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[\be]}
$$
If there exists gate identifier $g \in \gates(\prog_1)$ such that:
\begin{enumerate}
  \item $\owl(\prog_1,v_1,g)$
  \item $\gNIMO(\prog_1,v_2,g)$
\end{enumerate}
Then $\NIMO(\prog_1;\prog_2;\eassign{x}{\be})$.
\end{lemma}

>>>>

\section{A Protocol Metalanguage}
\label{section-metalang}

@@

### 2023-06-09 popl24/pmf.tex
checkpoint

\paragraph{Example \ref{example-lambda-obliv}(a) revisited} As demonstrated
by Example \ref{example-lambda-obliv} taken from \cite{XXX}, it is possible
to leak information probabilistically through obvservable dependencies
in views. In the basic distribution for Example \ref{example-lambda-obliv}(a)
illustrated in Figure \ref{fig-basic-distributions}, we can see that
the adversarial views $\vx{0}{0}$ and $\vx{0}{1}$ are both 1 in
three different runs of the protocol, and in 2 out of 3 the
honest secret $\sx{1}{0}$ is 1. More precisely:
$$
(\progd(\prog_{\ref{example-lambda-obliv}(a)}))(\{\sx{1}{0} \mapsto 1 \}|\{ \vx{0}{0} \mapsto 1, \vx{0}{1} \mapsto 1, \}) = 2/3
$$

>>>>

\paragraph{Example \ref{example-lambda-obliv}(a) revisited} As demonstrated
by Example \ref{example-lambda-obliv} taken from \cite{XXX}, it is possible
to leak information probabilistically through obvservable dependencies
in views. In the basic distribution for Example \ref{example-lambda-obliv}(a)
illustrated in Figure \ref{fig-basic-distributions}, we can see that
the adversarial views $\vx{0}{0}$ and $\vx{0}{1}$ are both 1 in
three different runs of the protocol, and in 2 out of 3 the
honest secret $\sx{1}{0}$ is 1. More precisely:
$$
(\progd(\prog_{\ref{example-lambda-obliv}(a)}))(\{\sx{1}{0} \mapsto 1 \}|\{ \vx{0}{0} \mapsto 1, \vx{0}{1} \mapsto 1 \}) = 2/3
$$
An important point illustrated by this example is that the
probability of values in views, and not just the values themselves,
can release information to the adversary.
